---
title: "Untitled"
output: html_document
---

Illustrate via simulation and associated explanatory text the properties of the distribution of the mean of 40 exponentials. You should

1. Show the sample mean and compare it to the theoretical mean of the distribution.

2. Show how variable the sample is (via variance) and compare it to the theoretical variance of the distribution.

3. Show that the distribution is approximately normal.

```{r}
# Task 1
library(ggplot2)
library(moments)

set.seed(42)

lambda <- 0.2

observation <- 40

TotalSimulation <- 1000


?replicate

simulated_exponential_Dist <- replicate(TotalSimulation , rexp(n = 40 , rate = lambda))

Simulated_means <- apply(simulated_exponential_Dist,MARGIN = 2 ,FUN = mean)
Simulated_means

sample_statistics_mean <- mean(Simulated_means)
sample_statistics_mean #  4.986508

theory_mean <- 1 / lambda
theory_mean # 5


# Let's Visualize it

ggplot2::ggplot(data = as.data.frame(Simulated_means) ,aes(x = Simulated_means))+
        ggplot2::geom_histogram(bins = 80,aes(y = ..density..)) +
        ggplot2::geom_vline(aes(xintercept = sample_statistics_mean,col = "blue",)) +
        ggplot2::geom_vline(aes(xintercept = theory_mean,col = "red",  )) + 
        ggplot2::geom_density(col = "red") + 
        ggplot2::labs(title = "Simulated Visualizations" , x = "means") 
      

paste("the analytics mean is " ,sample_statistics_mean , " the theoretical mean is 5. The center of sampling distribution of 40 exponentials is very close to the theoretical center of the distribution.")


```


```{r}

# Task 2 

#2. Show how variable the sample is (via variance) and compare it to the theoretical variance of  the distribution.


StandardDeviationSimulated <- sd(Simulated_means)
VarianceOfSimulated <- StandardDeviationSimulated ^ 2

TheoreticalStandardDeviations <- 1 / lambda/sqrt(observation)

VarianceOfTheoreticalStandardDeviations <- TheoreticalStandardDeviations ^2

paste("Theoretical Variance : " , VarianceOfTheoreticalStandardDeviations , "Simulated Variance" , VarianceOfSimulated)

# From here we know the distribution is nearly close same , but the true one is that the Simulated Variance

```
```{r}
ggplot2::ggplot(data = as.data.frame(Simulated_means) ,aes(x = Simulated_means))+
        ggplot2::geom_histogram(bins = 50,aes(y = ..density.. ),col = "black",fill="orange") +
        ggplot2::geom_density() +
        ggplot2::labs(title = paste("Simulated Visualizations Skewness :" ,moments::skewness(Simulated_means)), x = "means") 


## Due To CLT and the N >= 30 we assumme this follow the normal distribution
```


