---
title: "Untitled"
output: html_document
   
---

```{r}
library(statsr)
library(ggplot2)


data("ToothGrowth")

unique(ToothGrowth$dose)
str(ToothGrowth)

?ToothGrowth

ToothGrowth$dose <- as.factor(ToothGrowth$dose)

# Question Of Interest 
print("is Dose Level affected taken affecting the result ? ")
print("is there a correlation between Tooth Length supplement type by the dose level ?")
print("which is better for tooth length growth?")

# Summary Statistics 
summary(ToothGrowth$len)

summary(ToothGrowth$supp)

summary(ToothGrowth$dose)

table(ToothGrowth$supp ,ToothGrowth$dose)

```
# Explanatory Data Analysis
 Let's See What we have here 
 
```{r}
# Checking the Supplement Type
set.seed(4)
ggplot2::ggplot(data = ToothGrowth , aes(x = dose , y = len )) + 
        ggplot2::geom_boxplot(aes(fill = supp))+
        ggplot2::geom_point(aes(color=supp) , position = "jitter") + # because the dose is not always exact same , 
        ggplot2::scale_color_manual(values = c("purple","black")) + 
        ggplot2::scale_fill_manual(values = c("green","red")) +
        ggplot2::theme(legend.position=c(1,0.2),legend.justification=c(1,0.8)) +
        ggplot2::labs(title = "BoxPlot of Tooth Length and Dose by Supplement Type", y = "ToothLength", x ="Dose")
```

Let's do Inference print("is there a correlation between Tooth Length and supplement type ?")

```{r}
t.test(formula = len ~ supp , data = ToothGrowth , paired = FALSE , var.equal = F )


```

Because Our Null Hypothesis is 0 and our p_value is > 0.05 and the confidence interval contain the 0 , thus we can say there is no correlation between the supplement type,but is that true ? .

Let's do another Inference print("is there a correlation between Tooth Length and Supplement type based on dose level  ?")

```{r}
ToothGrowth$dose
doselevel05 <-ToothGrowth[ToothGrowth$dose == "0.5",]
doselevel2 <-ToothGrowth[ToothGrowth$dose == "2",]
doselevel1  <-ToothGrowth[ToothGrowth$dose == "1",]
t.test(formula = len ~ supp , data = doselevel05 , paired = F , var.equal = F)

```
Wait the confidence interval does not contain 0 , which mean there is a correlation here between supplement type and tooth length , so i guess the Dose taken seems to affect the tooth length

```{r}

t.test(formula = len ~ supp , data = doselevel1 , paired = F , var.equal = F)



```
Wait the confidence interval does not contain 0 , which mean there is a correlation here between supplement type and tooth length  ,it could be affect the length of Tooth , so i guess the Dose taken seems to affect the tooth length 


```{r}

t.test(formula = len ~ supp , data = doselevel2 , paired = F , var.equal = F) 
```
Ahh We Found it , seems  this guy here doesnt  correlated the tooth length ,for given people with high Dose level



## Assumptions Needed For The Conclusions:
- Members of the sample population, the 60 guinea pigs, are representative of the entire population of guinea pigs. This assumption Satisfied The Random Sample.
- For Each P and (p-1) is exactly >= 10 are satisfied to

For the t-tests, the variances are assumed to be different for the two groups being compared. This assumption is less stronger than the case in which the variances are assumed to be equal.

# Conclusion 
- 
- is Dose Level affected taken affecting the result ?  Yes, Increase in supplement Dose levels leads to overall increase in Tooth length on average.

-is there a correlation between Tooth Length supplement type by the dose level ? Yes ,Supplement method has no significant impact on Tooth length for doseLevel 2 ,but for doselevel 0.5 and 1 it seems there are a significant impact.

-"which is better for tooth length growth?Orange Juice increase a tooth length growth more fast compare the ascorbic acid